### 2018-04-10 Sections/encrypted_cloud_quantum_computing.tex
Added more stuff to XXIII.A.

\sihui{The first FHE scheme was reported in Gentry's seminal paper \cite{bib:gentry2009fully}. He showed that if a homomorphic encryption scheme can evaluate its own decryption circuit, and also slightly augmented versions of it--a feature he calls {\it bootstrapping}, one can construct a FHE scheme from it. Then he constructed a homomorphic encryption protocol using ideal lattices, and via a clever transformation that decreases the complexity of its decryption circuit, showed that it is bootstrappable with respect to a universal set of gates. For a security parameter $\lambda$, Gentry's scheme has a $\widetilde{O}(\lambda^6)$ \footnote{The tilde in the big O notation means that we are ignoring logarithmic factors.} bit bound on complexity for refreshing a ciphertext corresponding to a 1-bit plaintext \cite{bib:Gentrythesis}. This was subsequently reduced to $\widetilde{O}(\lambda^{3.5})$ \cite{bib:Damien2010}, $\widetilde{O}(\lambda)$ \cite{bib:Brakerski2011}, and ${\rm polylog (\lambda)}$ for any width-$\Omega(\lambda)$ circuit with $t$ gates \cite{bib:Craig2012}. }
%
% Homomorphic Encryption
%

>>>>

\sihui{The first FHE scheme was reported in Gentry's seminal paper \cite{bib:gentry2009fully}. He showed that if a homomorphic encryption scheme can evaluate its own decryption circuit, and also slightly augmented versions of it--a feature he calls {\it bootstrapping}, one can construct a FHE scheme from it. Then he constructed a somewhat homomorphic encryption protocol using ideal lattices, and via a clever transformation that decreases the complexity of its decryption circuit, showed that it is bootstrappable with respect to a universal set of gates. For a security parameter $\lambda$, Gentry's scheme has a $\widetilde{O}(\lambda^6)$ \footnote{The tilde in the big O notation means that we are ignoring logarithmic factors.} bit bound on complexity for refreshing a ciphertext corresponding to a 1-bit plaintext \cite{bib:Gentrythesis}. This was subsequently reduced to $\widetilde{O}(\lambda^{3.5})$ \cite{bib:Damien2010}, $\widetilde{O}(\lambda)$ \cite{bib:Brakerski2011}, and ${\rm polylog (\lambda)}$ for any width-$\Omega(\lambda)$ circuit with $t$ gates \cite{bib:Craig2012}. }

\sihui{A homomorphic encryption scheme is made up of four algorithms: a key generation algorithm, {\sc KeyGen}, an encryption algorithm, {\sc Encrypt}, an evaluation algorithm, {\sc Evaluate}, and a decryption algorithm, {\sc Decrypt}. The four algorithms have the following inputs and outputs:
\begin{itemize}
\item 	 {\sc KeyGen}$(\lambda)$: Takes as input a security parameter $\lambda$, and outputs a public key $pk$, and a secret key $sk$.
\item {\sc Encrypt}$(pk, \pi_i)$: Takes as input $pk$, and a plaintext $\pi_i$. It outputs a ciphertext $\psi_i$.
\item {\sc Evaluate}$(pk, C, \Psi)$: Takes as input $pk$, a permitted circuit $C$, and $\Psi=(\psi_1,\ldots, \psi_t)$. It outputs a ciphertext $\psi$.
\item {\sc Decrypt}$(sk,\psi)$: Takes as input $sk$, and $\psi$ and outputs $C(\pi_1,\ldots, \pi_t)$.
\end{itemize}
The computational complexity of all these algorithms must be polynomial in $\lambda$, and in the case of the evaluation algorithm, polynomial in the size of the evaluation circuit $C$. The condition that {\sc Decrypt}$(sk,\psi)$ outputs $C(\pi_1,\ldots, \pi_t)$ is a condition known as correctness which we require of the homomorphic encryption scheme. Furthermore, we also require ciphertext size and decryption time to be upper bounded by a function of the security parameter $\lambda$, independently of $C$. This last condition is known as compactness, and is necessary to exclude trivial schemes such as that which decrypts the ciphertexts first, and then apply $C$.}

\sihui{The specifics of these algorithm vary from scheme to scheme, and as in the case of FHE, usually contains sub-algorithms within them.}

%The Algorithm:Keygen

\begin{algorithm}
\caption{Key Generation algorithm}\label{euclid}
\begin{algorithmic}[1]
\Procedure{KeyGen($\lambda$)}{}
\BState \textbf{Input:} Security parameter $\lambda$
\BState \textbf{Output:} public key $pk$, secret key $sk$
\BState \emph{top}:
\If {$i > \textit{stringlen}$} \Return false
\EndIf
\State $j \gets \textit{patlen}$
\BState \emph{loop}:
\If {$\textit{string}(i) = \textit{path}(j)$}
\State $j \gets j-1$.
\State $i \gets i-1$.
\State \textbf{goto} \emph{loop}.
\State \textbf{close};
\EndIf
\State $i \gets i+\max(\textit{delta}
_1(\textit{string}(i)),\textit{delta}_2(j))$.
\EndProcedure
\end{algorithmic}
\end{algorithm}
